RadLib: a radiative property model library for combustion CFD

### 2021-07-22 submissions/CPC_response_to_reviewers.md

## Reviewer 3

The Computer Program in Physics (CPiP) submission titled, "RadLib: a radiative heat transfer model library for CFD" by Stephens et al reports a library of radiative property models that is modular and can be interfaced with other radiation model components. The manuscript is well-written and well-organized. The works cited are reasonable. RadLib contains a gray Planck-mean (PM) model, a weighted sum of gray gases (WSGG) model, and the rank-correlated SLW model. This is definitely an important tool for the combustion community, where the radiation modeling is often oversimplified mainly because of the lack of readily available appropriate radiation model libraries! I am not aware of any open-source libraries that combine the three property models presented here. The models included in RadLib are already well-established and well-validated in the radiation community. The library is written in C++ and is supposed to work in any Linux-like system. The code is well commented, although the associated documentation needs to be improved (see major comment #1).

Considering all these, I think that this CPiP submission is definitely within the scope of the journal and of interest to the research community. However, the following concerns must be addressed before the submission is considered for publication.

**The authors thank the reviewer for their insightful comments and suggestions. As members of the combustion community, we heartily agree that a tool like RadLib could benefit researchers and facilitate radiation model development for combustion CFD.**

@@

1) I could not successfully build and run the library in two different Linux systems. In both cases, first, the cmake returned an error:
"CMake Error at c++/CMakeLists.txt:34 (install): install TARGETS given no ARCHIVE DESTINATION for static library target "radlib"."
I could resolve this by adding ARCHIVE DESTINATION line on the c++/CMakeLists.txt file.
But, then on during "make" my installation was interrupted several times because of missing packages in my Python installation.
I would strongly recommend that the authors modify the installation instructions to include: a) list of dependencies (i.e., what compilers, what versions of python, what python packages, etc.), b) how to install the dependencies before building RadLib, c) a way to build RadLib with either only C++ or only Python. These installation notes do not necessarily need to be in the main manuscript, but they must be in the installation README of the code package.

	**The CMake build system has been updated such that ```ARCHIVE DESTINATION``` is explicitly specified, so that error should no longer occur. A build option has been added that makes the Python interface installation optional. Note that the C++ source code is required to install the Python interface, so there is no option to build only the Python interface. All of this information has been added to the ```README.md``` files located in the root directory and the ```build``` directory along with a more thorough list of software dependencies and required Python packages. Furthermore, we have now done full tests of the installation and running of all examples on a desktop Mac, a desktop Linux machine, and a large Linux-based cluster.**

@@

2) The library includes PM, one WSGG, and a RCSLW model. The authors should clearly indicate the rationale of these choices (i.e., why only these three models) early on in the manuscript. Since this is intended for researchers who, presumably, are not experts in radiation modeling, the inclusion of these three models can be misleading. One might think that these three models are the most appropriate models for their simulations.

	**Section 2 has been heavily revised to address this issue. Each model's description now also includes a discussion of its strengths, weaknesses, and limitations when applied to combustion CFD in addition to the authors' rationale in choosing them for RadLib.**

3) RadLib is intended to be expanded with new radiation property models in the future and interfaced with a user-supplied solver module for RTE. A brief discussion on how to interface such an external solver module should be presented. There is an example of a ray-tracing solver presented in the code files, but a brief discussion on coupling one's own RTE solver is important in the manuscript. Additionally, a brief discussion on how a user can add a new radiative property model should also be included.

	**Section 3 has been revised and extended to include more information on how users can include and interact with the RadLib library, including explicit references to example files that further illustrate usage of the library. We have also added a subsection to the results discussion that describes the integration of RadLib with the Fire Dynamics Simulator (FDS) code developed by NIST. Adding additional radiative property models to RadLib would require creating another class object for the implementation. The intention would be for the new model to inherit from the ```rad``` base class and reimplement the interface functions ```get_k_a``` and ```get_k_a_oneband```. Depending on the model, additional functionality may be needed. The Fortran and Python interfaces are wrapper functions that can be extended by paralleling the existing code, which is much simpler than writing these interfaces from scratch. A discussion on these points has been added to Section 3.**

@@

4) The Planck-mean absorption coefficient included in RadLib is based on TNF workshop data (from 2003). According to the references cited, these are fairly old correlations. If the authors use these data, I am concerned that the model parameters and correlations used in RadLib for the PM model may be obsolete and inaccurate. Can the authors please comment on this?

	**We purposely chose the TNF workshop data for calculating Planck Mean absorption coefficients because it is one of the most common and widely used radiation models applied to turbulent combustion simulations, despite its age and limitations. Section 2.1 has been revised to include a more explicit dicsussion of why the TNF radiation model was chosen and concerns related to its relative age and limited applicability. Section 4 includes example cases that clearly demonstrate the deficiencies of the PM model compared to the other models included with RadLib, and some additional discussion is available there. We intend to extend the model to include updated PM data.**

@@

5) On page 13, the authors present a paragraph describing Figs. 2 and 3 - the comparison of various radiation property models present in RadLib in one-dimensional configurations. The comparisons are presented simply as observations without any explanation or reasoning why the models behave the way as seen in Fig. 2 and 3. If I understand correctly, the focus of the work presented here is not the comparison of the accuracy of the three models but to showcase the library. Therefore, these comparisons - specifically without any explanation of the results - may not be essential to the current manuscript, and can be shortened. These results do serve as descriptions of example cases provided in RadLib. On the same page, the authors say that "While ommitted [should be omitted] here for brevity, the implemented WSGG and RCSLW models give essentially identical results to those presented in [11, 14] such that these examples also serve as a validation of the implementation of the
models." The authors should avoid qualitative description such as "essentially identical" in the context of validation and present a quantitative (e.g., % error) metric wherever possible. A strong validation is important for programs like this.

	**While it is true that the purpose of this paper is to present the RadLib library rather than evaluate or compare the models, the authors believe that example case results in Figures 2 and 3 are important. These illustrated examples RadLib's capabilities, demonstrate the example cases provided with the code, and provide comparison between the models and with reference to the LBL data. Comparison between the models has relevance to the reviewer's second comment above regarding the rationale of the models chosen, and our discussion of them in reply in the text. The reviewer's point about presentation without explanation is valid. The discussion in Section 5 has been expanded. Some of the results and discussion have changed since are now using updated parameters for the WSGG model that improves the agreement of that model, especially for Example S4. This makes the models for the different cases presented more consistent, lessening some of the burden for explaining anomolous behavior, though, due to the empirical nature of the PM and WSGG models, full explainations can still be difficult.**

    **Regarding validation, we agree with the reviewer in being careful about the language used. We are fully confident in the implementations of the models presented. Model parameters were checked and rechecked, and results from RadLib were carefully compared to the corresponding model results presenting in the original papers. In the case of the RCSLW model, which is the most complex to implement, we had the benefit of discussions with the inventors of the model (noted in the Acknowlegements), and even compared our code output to their Fortran implementation. We have modified the text to avoid qualitative description.**

@@

6) The computational cost tables for two cases show a significantly different trend, which the authors attribute to "additional overhead required in performing the calculations." Can the authors be more specific as to what these overheads may be? They say that they have neglected the initialization and input/output costs. Also, do these CPU times presented include the cost for the ray-tracing solver as well? Are the grids kept the same for all configurations?

    **We have modified the discussion slightly by moving the note about the cost not including model initialization and input/output earlier to make it clear that that applied to all results. Two cost comparisons are given: (1) cost of the property evaluation itself; and (2) cost of the full RTE solve (including the ray-tracing solution and property evaluation). Item (2) is relevant since property evaluations are not normally done in isolation, but part of a larger RTE solve, so that differences in the property model costs have less impact on the overall cost. This is now noted in the paper. The revision should be clear about the costs including the ray-tracing solver and the constant grids. Regarding the "overhead," the revision reorders the discussion and that word is not used. This discussion parallels what is noted here, that differences in the overall costs are smaller when accounting for the cost of the RTE solver as well as the property evaluation. (Note that Section 4.1 has since been moved to Section 5. It and the appropriate figure captions have also been revised for clearer communication of the points above.)**

@@

7) In line 53 on page 4, the authors claim to have CH4 property in RadLib but none of the validation cases contain CH4. Furthermore, for RCSLW, the refer to Pearson's work as a source for data of CO2, H2O, and CO without indicating the source data for CH4.

	**CH4 is present only in the PM model sourced from the TNF Workshop [3,5], which includes CH4 absorption coefficients because most of the TNF Workshop target flames are fueled by CH4. In general, CH4 is not a significant radiatively participating species in combustion systems, but it is included in the PM model for completeness with the PM source. The revision notes differences in the models and species, and default values are included for species in the interfaces (also now noted) so that users don't have to specify mole fractions for species that are not used in a given model.**

@@

MINOR:

1) It should be clarified that RadLib only provides radiation properties for non-scattering media.

	**This clarification has been made explicitly in Section 2 and now appears elsewhere the text where appropriate.**

@@

2) In the program summary the description of the nature of the program is somewhat confusing from a grammatical construction standpoint. Particularly, the following part, "This presents a problem for practitioners who wish to use/implement radiation models for which [refers to what?] such models consitute [constitute?] only a small but important part of a larger simulation.  Turbulent combustion simulations are one such example [example of what?].  Often, rudimentary assumptions [in what?] are made and this can negatively impact results."

	**The program summary has been rewritten for clarity.**

3) In Page 2, "In some cases, radiative gains or losses are small compared to other energy sources or heat transfer modes and radiation can be safely neglected, ... difficult to simulate accurately without a robust radiation model." Please provide some references to support these arguments.

	**This statement has been removed in the revision. In the spirit of this comment, we have added references to the text where needed to bolster weakly supported arguments. In particular, due to unrelated revisions, such discussion appears in Section 2.1 since it is most closely related to the Planck Mean model and its limitations.**

@@

5) Page, 4: "Global models are an important class of radiation property models that make use of spectrally-integrated radiation properties and are usually versions of the weighted sum of gray gases (WSGG) model [1, 2]." This sentence is somewhat misleading. It may be more appropriate to think of WSGG models as special cases of SLW or FSK models.

	**The authors agree that this statement could be potentially misleading. The second half of the sentence (beginning with ". . .and are usually. . .") has been removed.**

6) In lines 48-52 on Page 4, the authors say that the absorption coefficients are calculated using some correlations after some curve-fitting to spectroscopic databases. I am not sure what the authors refer to as correlations. There may be some correlations involved in WSGG models, but it is not clear to me where are correlations involved in RCSLW.

	**The absorption coefficients for the gray gases are developed from high resolution databased, and correlated, for each gray gas considered, as functions of the local gas state (temperature, pressure, and composition). The PM model uses a temperature correlation for each species absorbtion coefficient, with the overall absorption coefficient computed by combining the species. The WSGG model uses correlations developed for the gray gases based on emmivity calculations from the high resolution databases, and treats the composition through the molar H2O/CO2 ratio. The RCSLW model's key tool is the absorption line blackbody distribution function (ALBDF), which is calculated using spectral data available from databases like HITEMP. See Solvjov 2017 (cited in the paper) for details. The revision includes such discussions for the individual models. The modification of the original statement is in the last paragraph in Section 2 before section 2.1.**

@@

7) On page 7, the authors mention that the PM model can be "reasonably accurate" in some cases and go on to say that, "The Planck Mean model is most appropriate under optically thin conditions  with  relatively  low  radiative  transfer  relative  to  other  heat  sources such  as  reactive  heat  release  rates." The Planck Mean model will be appropriate in optically thin cases as there is very little reabsorption. This may or may not be connected with "relatively  low  radiative  transfer  relative  to  other  heat  sources." In fact, if the radiative heat transfer is much lower than chemical heat release, neglecting radiation altogether may also be reasonable! Although, the definition of "relatively low" is subjective.

    **This discussion is modified in the revision. The PM model is not directly connected to optical thickness of flames. In combustion applications, the PM model is often used in situations that are optically thin. In such cases, the radiative losses are relatively low (often around 5% for laboratory jet flames), and use of the PM model provides sufficient accuracy given that errors are active at the 5% level of the overall radiative losses, so not severe. When coupled with the optically thin assumption for RTE treatment, the radiative solve is relatively simple and inexpensive.**

@@

8) On the same page, lines 40-41, "This version of the WSGG model is advantageous because it allows for arbitrary CO2 and H2O compositions, increasing its accuracy and flexibility." Can the authors provide some references that show the increased accuracy and/or flexibility of this WSGG over any other WSGG?

	**Two references for the chosen WSGG model are given earlier in the paragraph. The second (Bordbar et al. 2020) includes detailed comparisons between this model, its immediate predecessor (see Bordbar et al. 2014), five other WSGG models, and line-by-line calculations for four different test cases that show high accuracy over a wide range of molar ratio values. While other models may have performed better in individual tests, this model demonstrated consistent accuracy over a range of scenarios. For clarity, this reference has been added to the end of the aforementioned sentence so as to better indicate where to obtain relevant information.**

9) With respect to Eqn 8, Mr is defined as molar ratio y_H2O/y_CO2. Are the authors using y as a symbol for mole fraction rather than mass fraction as is conventionally done?

    **We have changed the notation in the paper to use x instead of y. This is consistent with our use in the code, and we also prefer x for mole fraction and y for mass fraction. Solovjov (RCSLW) and Bordbar (WSGG) both use Y for mole fraction though.**

@@

11) In lines 29-30 on page 13, please insert the units for Q in -80 and 200.

	**Done.**

12) In the Discussion (page 16), the authors write, "Neglecting radiation or using simple models like the optically thin assumption is adequate for some cases with simple geometry or limited chemical reactions…" This can be misleading. I am not sure if either the simple geometry or the limited chemical reactions give any indication of the importance of radiation. Rather, something like a radiant fraction or optical thickness may be a more appropriate metric to justify neglecting radiation or using an optically thin model.

    **This is a good point. The revision should correct this. We partially answer this in reply to your comment above regarding page 7 that the "PM model can be 'reasonably accurate'". In particular, we are revising the discussion around the PM model to note that it is not an overly accurate model in comparison to the others, but it is widely used, and its use is warranted in situations with relatively low radiative losses that may occur, for example, in cases where radiative losses are low compared to heat release rates, or where flow timescales are low compared to radiative transfer timescales.**

### 2021-07-22 manuscript/manuscript.tex
DOL edits: done with responses to reviewers, which include some revisions to the paper. TODO: go through the paper start to finish and make edits. Some notes need to be implemented or verified in the paper to make sure the paper is consistent with the responses to reviewers.

\begin{small}
\noindent
{\em Program Title:} RadLib                                         \\
{\em CPC Library link to program files:} (to be added by Technical Editor) \\
{\em Developer's repository link:} https://github.com/BYUignite/radlib \\
{\em Code Ocean capsule:} https://codeocean.com/capsule/0997975/tree \\
{\em Licensing provisions(please choose one):} MIT \\
{\em Programming language:} C++, Python                                   \\
{\em Nature of problem(approx. 50-250 words):} \\
Radiative heat transfer in combustion CFD problems is typically neglected or oversimplified, resulting in significant error and inaccuracy in combustion simulations. Radiation modeling, however, often requires a high degree of specialization due to its complexity and the challenges associated with implementation in existing CFD codes, which presents a substantial obstacle to researchers who wish to address the inaccuracies introduced by insufficient radiative heat transfer modeling in combustion simulations. \\
{\em Solution method(approx. 50-250 words):}\\
We present RadLib, an open-source C++ library of validated radiation property models that can be applied alongside various RTE solution methods to ease some of the obstacles associated with radiation modeling for combustion CFD. The package includes multiple interface options (C++ and Python), several illustrative examples with a provided ray-tracing solver, and a framework for expansion to include additional radiation property models and interfaces.\\ 
{\em Additional comments including restrictions and unusual features (approx. 50-250 words):}\\
The library is intended to be used in Linux-like terminal applications.  
   \\

@@

Radiation absorption coefficients are typically calculated via correlations developed from high-resolution spectral databases like RADCAL, HITEMP, and HITRAN \citep{Grosshandler_1993,Rothman_2010} that relate spectral line strength to properties such as temperature, pressure, and gas composition \citep{Zhang_2002b}. At present, RadLib considers up to four gas species (H$_2$O, CO, CO$_2$, and CH$_4$) and soot. Note that the property models implemented in RadLib apply only to non-scattering media.

@@

Weighted sum of gray gases (WSGG) models generate radiation absorption coefficients for use with the spectrally integrated RTE (Eq.~\ref{e:RTE_wsgg}).
RadLib implements the WSGG model presented by Bordbar et al. \citep{Bordbar_2014,Bordbar_2020}, which uses correlations based on the HITEMP 2010 database \cite{Rothman_2010}. It models mixtures of gaseous \ce{CO2} and \ce{H2O}, the two most significant radiatively participating species in most combustion environments, using four gray gases and one clear gas. Absorption coefficients are calculated by 
%
\begin{linenomath}
\begin{equation}
    \kappa_j=\sum_{k=0}^{4}d_{j,k}M_r^k,
\end{equation}
\end{linenomath}
%
where $\kappa_j$ is the absorption coefficient for gray gas $j$, $d_{j,k}$ is a correlated model coefficient, and $M_r$ is the molar ratio $y_{\mathrm{H_2O}}/y_{\mathrm{CO_2}}$. The weight factors are calculated by 
%
\begin{linenomath}
\begin{equation}
    a_j=\sum_{k=0}^{4}b_{j,k}T_r^k,
\end{equation}
\end{linenomath}
%
where $a_j$ is the weighting factor for gas $j$ and $T_r$ is a scaled temperature equal to $T/T_{ref}$ with $T_{ref}=1200$K. The valid temperature range of the model is 300-2400 K; temperatures outside this range use the value at the respective bound. The value of $b_{i,j}$ is calculated by 
%
\begin{linenomath}
\begin{equation}
 b_{j,k}=\sum_{i=0}^{4}C_{j,k,i}M_r^i,
\end{equation}
\end{linenomath}
%
where $C_{j,k,i}$ is another correlated model coefficient. The model coefficients $d_{j,k}$ and $C_{j,k,i}$ are provided by Bordbar et~al. \citep{Bordbar_2014,Bordbar_2020} but updated values are used in RadLib.

@@

For multicomponent gas mixtures, the mixture absorption cross section $C_{\eta}$ is defined as a weighted sum of its component absorption cross sections \cite{Solovjov_2000}. RadLib's RCSLW implementation considers \ce{H2O}, \ce{CO2}, and \ce{CO}, for which the mixture absorption cross section for a given gray gas is given by 
%
\begin{linenomath}
	\begin{equation} \label{e:multiC}
		C_{\eta} = Y_{\ce{CO2}}C_{\ce{CO2},\eta} + Y_{\ce{H2O}}C_{\ce{H2O},\eta} + Y_{\ce{CO}}C_{\ce{CO},\eta}
	\end{equation}
\end{linenomath}
%
Assuming that the absorption cross sections of each species are statistically independent, we can calculate the mixture ALBDF for a given gray gas using the multiplication method \cite{Solovjov_2000}:
%
\begin{linenomath}
\begin{equation} \label{e:multiF}
    F_{\eta}(C_{\eta}) = F_{\ce{CO2},\eta} \left( \frac{C_{\eta}}{Y_{\ce{CO2}}} \right) F_{\ce{H2O},\eta} \left( \frac{C_{\eta}}{Y_{\ce{H2O}}} \right) F_{\ce{CO},\eta} \left( \frac{C_{\eta}}{Y_{\ce{CO}}} \right). 
\end{equation}
\end{linenomath}
%
Note that the $\BS{\phi}$ and $T$ arguments of $F$ are omitted from Eq.~\ref{e:multiF} for clarity.

@@

Given the concepts summarized above, the RCSLW model is applied to a problem of interest to calculate radiation absorption coefficients and weights as follows:
%
\begin{enumerate}
    \item Specify a reference temperature $T_r$ as the average temperature on the domain of interest \cite{Solovjov_2001}. Note that this is not the same as specifying a reference state $\BS{\phi}=\BS{\phi}_r(T_r,Y_r,P_r)$ as in done for SLW reference approaches. The RCSLW model has the significant advantage that it does not require a thermodynamic reference state.
    \item Specify a collection of $F_j$ points and $\tilde{F}_j$ boundary values such that $F_j$ lies between $\tilde{F}_j$ and $\tilde{F}_{j-1}$. These apply to all spatial positions. 
    \item Invert the ALBDF to calculate $C_j$ and $\tilde{C}_j$ at the corresponding thermodynamic state $\BS{\phi}$ and any spatial position where $C_j = C(F_j,\BS{\phi},T_r)$ and $\tilde{C}_j = C(\tilde{F}_j,\BS{\phi},T_r)$
    \item Compute the gray gas absorption coefficients $\kappa_j=C_jN$. 
    \item Compute the gray gas weights $a_j=F(\tilde{C}_j,\BS{\phi}, T) - F(\tilde{C}_{j-1},\BS{\phi}, T)$ (Eq.~\ref{e:aj}) with the $C_j$ and $\tilde{C}_j$ values calculated in Step 3, the local thermodynamic state $\BS{\phi}$, and the local temperature $T$.
\end{enumerate}

@@

The code installation folder includes directories \texttt{include} containing header files and a Fortran module file, 
\texttt{lib} containing library files for each interface, and \texttt{rcslw\textunderscore data} containing binary data files used by the RCSLW model. These binary files contain the ALBDF functions for a given species at a given pressure (in atm units), as indicated by the file name. The \texttt{include} directory contains the following interface header and module (Fortran) files:
%
\begin{itemize}
    \item \texttt{rad\textunderscore planck\textunderscore mean.h},
    \item \texttt{rad\textunderscore wsgg.h},
    \item \texttt{rad\textunderscore rcslw.h},
    \item \texttt{rad\textunderscore module.mod}.
\end{itemize}
%
The C++ and Fortran libraries in the \texttt{lib} folder are
\begin{itemize}
    \item \texttt{libradlib.a},
    \item \texttt{libradlib\textunderscore fortran.a},
\end{itemize}
%
This folder also contains the Python module.
The code installation additionally generates relocatable CMake files for downstream usage, located at \texttt{\seqsplit{installed/cmake/radlib/radlib.cmake}} and \texttt{\seqsplit{installed/cmake/radlib\textunderscore fortran/radlib\textunderscore fortran.cmake}}, where \texttt{installed/} may be replaced with a user-specified installation path. If the Python interface is built, the location of the installed Python package needs to be added to the \texttt{PYTHONPATH} environment variable. A command to do this is provided at the end of the installation, for example, \texttt{\seqsplit{export\ PYTHONPATH="/home/user/radlib/installed/lib/python3.8/site-packages:\$PYTHONPATH"}}.

@@

Figure \ref{fig:flowchart} illustrates the basic structure of using of RadLib in a generic one-dimensional RTE solution. The RadLib library generates absorption coefficients and their weighting factors for use within an appropriate RTE solver. A user first creates a radiation object, and then makes calls to one of two primary functions: \texttt{get\textunderscore k\textunderscore a()}, or \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()}.
These two functions take the arguments for temperature (K), pressure (Pa), soot volume fraction, and mole fractions of \ce{H2O}, \ce{CO2}, \ce{CO}, and \ce{CH4}. The WSGG model does not account for \ce{CO} or \ce{CH4}, and only the PM model includes \ce{CH4}. A uniform interface is facilitated by giving default values of 0.0 for the \ce{CO} and \ce{CH4} mole fraction parameters. The \texttt{get\textunderscore k\textunderscore a()} function computes a vector of absorption coefficients and a vector of weight factors, with elements corresponding to each clear and gray gas considered in the model (with the clear gas coming first). The PM model only considers one gas and the vectors are of unity size. The \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()} computes the absorption coefficient and weight factor (as scalar values) for a single gas (or \emph{band}), whose index (starting at zero for all interfaces) is provided as an additional argument. This option to compute the properties for a single gas/band can be important for efficient implementation in some solvers, e.g., in the Fire Dynamics Simulation (FDS), discussed below \cite{FDS}. The absorption coefficients and weights are set through the function argument list for the C++ and Fortran interfaces, and as return values for the Python interface. Additional details are included in the program documentation and code listing.
%
\begin{figure}
	\begin{center}
        \includegraphics[width=\textwidth]{fig_radlib_structure.pdf}
	\end{center}
	\caption{Example workflow diagram. Highlighted areas are part of the RadLib library; other areas represent example infrastructure for using the package.}
\label{fig:flowchart}
\end{figure}
%

@@

These cases are intended to illustrate the use of the RadLib library and are not exhaustive. Details about these examples and their motivations can be found in their respective references. Comparison of these results to the LBL data and to the results presented in the source references also serves as a validation of RadLib's implementation of the WSGG and RCSLW models.

@@

In addition to comparing model attributes and performance, we evaluated and compared the computational cost of the implemented radiation property models. 
Calculations were performed on a 4 GHz Quad Core Intel Core i7 iMac, version 10.15.7; the results, normalized by the cost of the WSGG model, are summarized in Figure~\ref{f:cost}.

>>>>

\begin{small}
\noindent
{\em Program Title:} RadLib                                         \\
{\em CPC Library link to program files:} (to be added by Technical Editor) \\
{\em Developer's repository link:} https://github.com/BYUignite/radlib \\
{\em Code Ocean capsule:} https://codeocean.com/capsule/0997975/tree \\
{\em Licensing provisions(please choose one):} MIT \\
{\em Programming language:} C++, Fortran, Python \\
{\em Nature of problem(approx. 50-250 words):} \\
Radiative heat transfer in combustion CFD problems is typically neglected or oversimplified, resulting in significant error and inaccuracy in combustion simulations. Radiation modeling, however, often requires a high degree of specialization due to its complexity and the challenges associated with implementation in existing CFD codes, which presents a substantial obstacle to researchers who wish to address the inaccuracies introduced by insufficient radiative heat transfer modeling in combustion simulations. \\
{\em Solution method(approx. 50-250 words):}\\
We present RadLib, an open-source C++ library of validated radiation property models that can be applied alongside various RTE solution methods to ease some of the obstacles associated with radiation modeling for combustion CFD. The package includes C++, Fortran, and Python interfaces, several illustrative examples with a provided ray-tracing solver, and possibility for expansion to include additional radiation property models and interfaces.\\ 
{\em Additional comments including restrictions and unusual features (approx. 50-250 words):}\\
The library is intended to be used in Linux-like terminal applications.  
   \\

@@

Radiation absorption coefficients are typically calculated via correlations developed from high-resolution spectral databases like RADCAL, HITRAN, and HITEMP \citep{Grosshandler_1993,Rothman_2010} that relate spectral line strength to properties such as temperature, pressure, and gas composition \citep{Zhang_2002b}. At present, RadLib considers up to four gas species (H$_2$O, CO, CO$_2$, and CH$_4$), depending on the model, and soot. Note that the property models implemented in RadLib apply only to non-scattering media.

@@

Weighted sum of gray gases (WSGG) models generate radiation absorption coefficients for use with the spectrally integrated RTE (Eq.~\ref{e:RTE_wsgg}).
RadLib implements the WSGG model presented by Bordbar et al. \citep{Bordbar_2014,Bordbar_2020}, which uses correlations based on the HITEMP 2010 database \cite{Rothman_2010}. It models mixtures of gaseous \ce{CO2} and \ce{H2O}, the two most significant radiatively participating species in most combustion environments, using four gray gases and one clear gas. Absorption coefficients are calculated by 
%
\begin{linenomath}
\begin{equation}
    \kappa_j=\sum_{k=0}^{4}d_{j,k}M_r^k,
\end{equation}
\end{linenomath}
%
where $\kappa_j$ is the absorption coefficient for gray gas $j$, $d_{j,k}$ is a correlated model coefficient, and $M_r$ is the molar ratio $x_{\mathrm{H_2O}}/x_{\mathrm{CO_2}}$. The weight factors are calculated by 
%
\begin{linenomath}
\begin{equation}
    a_j=\sum_{k=0}^{4}b_{j,k}T_r^k,
\end{equation}
\end{linenomath}
%
where $a_j$ is the weighting factor for gas $j$ and $T_r$ is a scaled temperature equal to $T/T_{ref}$ with $T_{ref}=1200$K. The valid temperature range of the model is 300-2400 K; temperatures outside this range use the value at the respective bound. The value of $b_{i,j}$ is calculated by 
%
\begin{linenomath}
\begin{equation}
 b_{j,k}=\sum_{i=0}^{4}C_{j,k,i}M_r^i,
\end{equation}
\end{linenomath}
%
where $C_{j,k,i}$ is another correlated model coefficient. The model coefficients $d_{j,k}$ and $C_{j,k,i}$ are provided by Bordbar et~al. \citep{Bordbar_2014,Bordbar_2020} but updated values are used in RadLib.

@@

For multicomponent gas mixtures, the mixture absorption cross section $C_{\eta}$ is defined as a weighted sum of its component absorption cross sections \cite{Solovjov_2000}. RadLib's RCSLW implementation considers \ce{H2O}, \ce{CO2}, and \ce{CO}, for which the mixture absorption cross section for a given gray gas is given by 
%
\begin{linenomath}
	\begin{equation} \label{e:multiC}
		C_{\eta} = x_{\ce{CO2}}C_{\ce{CO2},\eta} + x_{\ce{H2O}}C_{\ce{H2O},\eta} + x_{\ce{CO}}C_{\ce{CO},\eta},
	\end{equation}
\end{linenomath}
%
where $x$ denotes mole fraction.
Assuming that the absorption cross sections of each species are statistically independent, we can calculate the mixture ALBDF for a given gray gas using the multiplication method \cite{Solovjov_2000}:
%
\begin{linenomath}
\begin{equation} \label{e:multiF}
    F_{\eta}(C_{\eta}) = F_{\ce{CO2},\eta} \left( \frac{C_{\eta}}{x_{\ce{CO2}}} \right) F_{\ce{H2O},\eta} \left( \frac{C_{\eta}}{x_{\ce{H2O}}} \right) F_{\ce{CO},\eta} \left( \frac{C_{\eta}}{x_{\ce{CO}}} \right). 
\end{equation}
\end{linenomath}
%
Note that the $\BS{\phi}$ and $T$ arguments of $F$ are omitted from Eq.~\ref{e:multiF} for clarity.

@@

Given the concepts summarized above, the RCSLW model is applied to a problem of interest to calculate radiation absorption coefficients and weights as follows:
%
\begin{enumerate}
    \item Specify a reference temperature $T_r$ as the average temperature on the domain of interest \cite{Solovjov_2001}. Note that this is not the same as specifying a reference state $\BS{\phi}=\BS{\phi}_r(T_r,x_r,P_r)$ as in done for SLW reference approaches. The RCSLW model has the significant advantage that it does not require a thermodynamic reference state.
    \item Specify a collection of $F_j$ points and $\tilde{F}_j$ boundary values such that $F_j$ lies between $\tilde{F}_j$ and $\tilde{F}_{j-1}$. These apply to all spatial positions. 
    \item Invert the ALBDF to calculate $C_j$ and $\tilde{C}_j$ at the corresponding thermodynamic state $\BS{\phi}$ and any spatial position where $C_j = C(F_j,\BS{\phi},T_r)$ and $\tilde{C}_j = C(\tilde{F}_j,\BS{\phi},T_r)$
    \item Compute the gray gas absorption coefficients $\kappa_j=C_jN$. 
    \item Compute the gray gas weights $a_j=F(\tilde{C}_j,\BS{\phi}, T) - F(\tilde{C}_{j-1},\BS{\phi}, T)$ (Eq.~\ref{e:aj}) with the $C_j$ and $\tilde{C}_j$ values calculated in Step 3, the local thermodynamic state $\BS{\phi}$, and the local temperature $T$.
\end{enumerate}

@@

The code installation folder includes directories \texttt{include} containing header files and a Fortran module file, 
\texttt{lib} containing library files for each interface, and \texttt{rcslw\textunderscore data} containing binary data files used by the RCSLW model. These binary files contain the ALBDF functions for a given species at a given pressure (in atm units), as indicated by the file name. The \texttt{include} directory contains the following interface header and module (Fortran) files:
%
\begin{itemize}
    \item \texttt{rad\textunderscore planck\textunderscore mean.h},
    \item \texttt{rad\textunderscore wsgg.h},
    \item \texttt{rad\textunderscore rcslw.h},
    \item \texttt{rad\textunderscore module.mod}.
\end{itemize}
%
The C++ and Fortran libraries in the \texttt{lib} folder are
\begin{itemize}
    \item \texttt{libradlib.a},
    \item \texttt{libradlib\textunderscore fortran.a}.
\end{itemize}
%
This folder also contains the Python module.
The code installation additionally generates relocatable CMake files for downstream usage, located at \texttt{\seqsplit{installed/cmake/radlib/radlib.cmake}} and \texttt{\seqsplit{installed/cmake/radlib\textunderscore fortran/radlib\textunderscore fortran.cmake}}, where \texttt{installed/} may be replaced with a user-specified installation path. If the Python interface is built, the location of the installed Python package needs to be added to the \texttt{PYTHONPATH} environment variable. A command to do this is provided at the end of the installation, for example, \texttt{\seqsplit{export\ PYTHONPATH="/home/user/radlib/installed/lib/python3.8/site-packages:\$PYTHONPATH"}}.

@@

Figure \ref{fig:flowchart} illustrates the basic structure of using of RadLib in a generic one-dimensional RTE solution. The RadLib library generates absorption coefficients and their weighting factors for use within an appropriate RTE solver. A user first creates a radiation object, and then makes calls to one of two primary functions: \texttt{get\textunderscore k\textunderscore a()}, or \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()}.
These two functions take the arguments for temperature (K), pressure (Pa), soot volume fraction, and mole fractions of \ce{H2O}, \ce{CO2}, \ce{CO}, and \ce{CH4}. The WSGG model does not account for \ce{CO} or \ce{CH4}, and only the PM model includes \ce{CH4}. A uniform interface is facilitated by giving default values of 0.0 for the \ce{CO} and \ce{CH4} mole fraction parameters. The \texttt{get\textunderscore k\textunderscore a()} function computes a vector of absorption coefficients and a vector of weight factors, with elements corresponding to each clear and gray gas considered in the model (with the clear gas coming first). The PM model only considers one gas and the vectors are of unity size. The \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()} computes the absorption coefficient and weight factor (as scalar values) for a single gas (or \emph{band}), whose index argument (starting at zero for all interfaces) is provided as an additional argument. This option to compute the properties for a single gas/band can be important for efficient implementation in some solvers, e.g., in the Fire Dynamics Simulation (FDS), discussed below \cite{FDS}. The absorption coefficients and weights are set through the function argument list for the C++ and Fortran interfaces, and as return values for the Python interface. Additional details are included in the program documentation and code listing.
%
\begin{figure}
	\begin{center}
        \includegraphics[width=\textwidth]{fig_radlib_structure.pdf}
	\end{center}
	\caption{Example workflow diagram. Highlighted areas are part of the RadLib library; other areas represent example infrastructure for using the package.}
\label{fig:flowchart}
\end{figure}
%

The RadLib source code is build around a base class called \texttt{rad} from which the individual property models, e.g., \texttt{rad\textunderscore rcslw}, inherit.
To extend RadLib to include new radiative property models, a user would create a new derived class for the model that inherits from the \texttt{rad} base class. The interface functions \texttt{get\textunderscore k\textunderscore a} and \texttt{get\textunderscore k\textunderscore a\textunderscore oneband} would be reimplemented in the new model. Additional functions and capabilities could be added as desired. The Fortran and Python interface codes consist of wrapper functions to the underlying C++. These can be easily extended by paralleling the existing interface functions.

@@

These cases are intended to illustrate the use of the RadLib library and are not exhaustive. Details about these examples and their motivations can be found in their respective references. Comparison of these results to the LBL data, shown here, serve as model validation. For WSGG and RCSLW, direct comparison (not shown) of RadLib was made to examples presented in the model references with identical results (up to the resolution of the available data), which serves as verification of the implementation.

@@

In addition to comparing model attributes and performance, we evaluated and compared the computational cost of the implemented radiation property models. 
Calculations were performed on a 4 GHz Quad Core Intel Core i7 iMac, version 10.15.7; the results, normalized by the cost of the WSGG model, are summarized in Figure~\ref{f:cost}. 
In the results presented, only the cost of evaluating the solution was included; model initialization and input/output costs were neglected. In the results including the ray-tracing solver, the same number of rays and grid points is used in all calculations.
